project 1

### 2017-01-09 project_1.Rmd
made link in glm explicit

### Logistic Regression
```{r}
prostate_logreg <- glm(`Erectile Function at 2 years` ~ Age + `Gleason Score` + `T-Stage Group` + PSA + HRQOL + ADT + BMI + `Erectile Function at Baseline`, data = prostate)
# summary(prostate_logreg)
kable(tidy(prostate_logreg))
prostate <- prostate[, predicted_prob := predict(prostate_logreg)]
prostate <- prostate[, predicted := ifelse(predicted_prob >= 0.5, 1, 0)]
error_rate <- prostate[, sum(abs(predicted - `Erectile Function at 2 years`))]/dim(prostate)[1]
error_rate

@@

#### Logistic regression on subsets of the data
```{r}
func_at_baseline <- prostate[`Erectile Function at Baseline` == 1] # subset only rows in which the men had erectile function at baseline 
sub_logreg <- glm(`Erectile Function at 2 years` ~ Age + `Gleason Score` + `T-Stage Group` + PSA + HRQOL + ADT + BMI + `Erectile Function at Baseline`, data = func_at_baseline)
kable(tidy(sub_logreg))
func_at_baseline <- func_at_baseline[, predicted_prob := predict(prostate_logreg)]
func_at_baseline <- func_at_baseline[, predicted := ifelse(predicted_prob >= 0.5, 1, 0)]
error_rate <- func_at_baseline[, sum(abs(predicted - `Erectile Function at 2 years`))]/dim(prostate)[1]
error_rate
```

>>>>

### Logistic Regression
```{r}
prostate_logreg <- glm(`Erectile Function at 2 years` ~ Age + `Gleason Score` + `T-Stage Group` + PSA + HRQOL + ADT + BMI + `Erectile Function at Baseline`, family = binomial(link = "logit") ,data = prostate)
# summary(prostate_logreg)
kable(tidy(prostate_logreg))
prostate <- prostate[, predicted_prob := predict(prostate_logreg)]
prostate <- prostate[, predicted := ifelse(predicted_prob >= 0.5, 1, 0)]
error_rate <- prostate[, sum(abs(predicted - `Erectile Function at 2 years`))]/dim(prostate)[1]
error_rate

@@

#### Logistic regression on subsets of the data
```{r}
func_at_baseline <- prostate[`Erectile Function at Baseline` == 1] # subset only rows in which the men had erectile function at baseline 
sub_logreg <- glm(`Erectile Function at 2 years` ~ Age + `Gleason Score` + `T-Stage Group` + PSA + HRQOL + ADT + BMI + `Erectile Function at Baseline`, family = binomial(link = "logit"), data = func_at_baseline)
kable(tidy(sub_logreg))
func_at_baseline <- func_at_baseline[, predicted_prob := predict(sub_logreg)]
func_at_baseline <- func_at_baseline[, predicted := ifelse(predicted_prob >= 0.5, 1, 0)]
error_rate <- func_at_baseline[, sum(abs(predicted - `Erectile Function at 2 years`))]/dim(prostate)[1]
error_rate
```
